### 2019-10-29 Paper_shortened_pdf.Rmd
Fix income

Our target sample consisted of 1884 native `r masked("Australian")`, non-minority, intact, biological families. At the first wave, children were approximately 6 years old, $M = 6.28$, $SD = .45$, and 12 at the final wave ($M = 12.42$, $SD = .49$); on agerage, mothers were 34.89 ($SD = 4.71$), and fathers 36.94 ($SD = 5.48$). Most families were dual-earner families, based on income from wages or enterprise ($N = 1067$; 669 father-only, 41 mother-only). The modal annual income for fathers was between \$26,000-\$51,999 (N = 663), and for mothers, \$25,999 or less per year (N = 1152).

>>>>

Our target sample consisted of 1884 native `r masked("Australian")`, non-minority, intact, biological families. At the first wave, children were approximately 6 years old, $M = 6.28$, $SD = .45$, and 12 at the final wave ($M = 12.42$, $SD = .49$); on agerage, mothers were 34.89 ($SD = 4.71$), and fathers 36.94 ($SD = 5.48$). Most families were dual-earner families, based on income from wages or enterprise ($N = 1067$); the remainder were single-earner families($N = 669$ father-only, $N = 41$ mother-only). The modal annual income for fathers was between \$26,000-\$51,999 (N = 663), and for mothers, \$25,999 or less per year (N = 1152).
